---
title: "Diff Tools"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{diff-tools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette demonstrates using a variety of `diff-` functions to assist with
QC efforts. All functions provide a visual difference of modifications to scripts.
The functions covered below include:

- `diffQced()` shows modifications to a script since it was last QCed.
- `diffPreviousRevisions()` shows modifications between versions of the same script.
- `diffFiles()` shows modifications between two scripts.

# Load libraries

```{r, message=FALSE}
library(review)
```

# Setup

For the purposes of this vignette, a demo SVN repository and files were created
using the `demoRepo()` function. The files in this repository are versioned 
and have past QC history.

```{r}
repo <- demoRepo("examp-123")
```

# diffQced

`diffQced()` generates a visual diff in the Viewer pane in R studio. 
All deleted, added and modified lines of code are shown in the diff. 

`diffQced()` uses the QC log to identify the revision number when the last QC 
was completed. The difference is then generated using the version of the file at 
that revision number versus the current file.

For this example, we will look at the modifications made to `script/data-assembly.R`
since its last QC.

```{r eval=FALSE}
diffQced("script/data-assembly.R")
```

```{r echo=FALSE, message=FALSE, results='asis'}
curdir <- getwd()
on.exit(setwd(curdir))
setwd(repo)
svnExport("script/data-assembly.R", 1)

diffobj::diffFile(
        "data-assembly-1.R",
        "script/data-assembly.R",
        color.mode = "rgb",
        ignore.white.space = FALSE,
        mode = "sidebyside",
        tar.banner="Revision 1",
        cur.banner="Local",
        format = "html",
        style = list(html.output = "diff.w.style"),
        interactive = F
      )
```

# diffPreviousRevisions

`diffPreviousRevisions()` generates a similar visual, except the versions 
of the scripts being compared can be explicitly defined. 

For any script, a previous and current revision number can be set to decide
the versions being used. If a current revision number is not provided, the 
default will be set to the most recent version of the script.

For this example, we can use the `script/pk/load-spec.R` script. We can view
the history of this file with `svnLog()`.

```{r eval=FALSE}
svnLog("script/pk/load-spec.R")
```

```{r echo=FALSE}
curdir <- getwd()
on.exit(setwd(curdir))
setwd(repo)
svnLog("script/pk/load-spec.R")
```

Now using `diffPreviousRevisions()`, we can look at the differences between 
the file at revisions 1 and 4.

```{r eval=FALSE}
diffPreviousRevisions(
    .file = "script/pk/load-spec.R",
    .current_revision = 4,
    .previous_revision = 1)
```

```{r echo=FALSE, message=FALSE, results='asis'}
curdir <- getwd()
on.exit(setwd(curdir))
setwd(repo)
svnExport("script/pk/load-spec.R", 1)

diffobj::diffFile(
        "load-spec-1.R",
        "script/pk/load-spec.R",
        color.mode = "rgb",
        ignore.white.space = FALSE,
        mode = "sidebyside",
        tar.banner="Revision 1",
        cur.banner="Local",
        format = "html",
        style = list(html.output = "diff.w.style"),
        interactive = F
      )
```

# diffFiles

`diffFiles()` generates a visual diff between two files. The first file 
provided will be treated as the past version when generating the visual diff.

For this example, we can use the `script/combine-da.R` and 
`script/data-assembly.R` scripts.

```{r eval=FALSE}
diffFiles(
  .file_1 = "script/combine-da.R", 
  .file_2 = "script/data-assembly.R"
)
```

```{r echo=FALSE, message=FALSE, results='asis'}
curdir <- getwd()
on.exit(setwd(curdir))
setwd(repo)

diffobj::diffFile(
        "script/combine-da.R",
        "script/data-assembly.R",
        color.mode = "rgb",
        ignore.white.space = FALSE,
        mode = "sidebyside",
        tar.banner="Revision 1",
        cur.banner="Local",
        format = "html",
        style = list(html.output = "diff.w.style"),
        interactive = F
      )
```