---
title: "SVN Helpers"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{svn-helpers}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is a vignette to help you become familiar with using `svnLog()` and 
`svnExport()`.

- `svnLog()` provides the history of all edits made to a file, including the
author, revision and date/time of the commit. 
- `svnExport()` makes it easy to restore a file to a previous revision.

Below we will go through examples of both, including cases where the information
from `svnLog()` can be used to more efficiently use `svnExport()`. 

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Load libraries

```{r, message=FALSE}
library(review)
```

# svnLog

For the purposes of this vignette, a demo SVN repository and files were created
using the `demoRepo()` function. We will look at the history of 
`script/data-assembly.R`.

To figure out when modifications were made to this file, we can use `svnLog()`.

```{r}
repo <- demoRepo("examp-123")
svnLog(file.path(repo, "script/data-assembly.R"))
```

Notice how the output data.frame is sorted such that the most recent commit is
shown on the first row. We can see every author and revision number where the 
file was modified and checked into SVN. 

# svnExport

Now that we know the revision numbers, we can use `svnExport()` to view any of
the previous revisions. First we can look at what the current version of 
`script/data-assembly.R` looks like:

```{r}
readLines(file.path(repo, "script/data-assembly.R"))
```

Then, we can use `svnExport()` to view the first revision of the file.

```{r, eval=FALSE}
svnExport(.file = file.path(repo, "script/data-assembly.R"), .revision = 1)
```

```{r, include=FALSE}
curdir <- getwd()
on.exit(setwd(curdir))
setwd(repo)
svnExport(.file = "script/data-assembly.R", .revision = 1)
```

Notice how this creates a new file, `test-file-1.txt` in the SVN directory.

```{r}
file.exists(file.path(repo, "data-assembly-1.R"))
```

Now we can take a look at the first revision of the file.

```{r, eval=FALSE}
readLines(file.path(repo, "data-assembly-1.R"))
```

```{r, echo=FALSE}
curdir <- getwd()
on.exit(setwd(curdir))
setwd(repo)
readLines("data-assembly-1.R")
```

This process can be done for any file that has been checked into your SVN
repository. `svnLog()` can easily identify the revision numbers of past edits
and `svnExport()` can restore the file with a file name following this syntax
[{original file name}-{revision number}].